The population of long-period exoplanets I. --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive

### 2016-03-02 document/ms.tex
some words about injections

@@

\begin{eqnarray}
Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k}}{a_k(\params)} \\
&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}\,P^{-2/3}
\end{eqnarray}

@@

\begin{eqnarray}
Q_{\mathrm{temp},k} (\params) &=& \frac{T_k}{P}
\end{eqnarray}
where $T_k$ is the total observing baseline for target $k$.
Combined with the detection efficiency $Q_{\mathrm{det}}(\params)$ (assumed to
be constant for each target), the total completeness as a function of the
parameters is
\begin{eqnarray}
Q_k(\params) &=& Q_{\mathrm{det},k}(\params) \,
                 Q_{\mathrm{temp},k} (\params) \,
                 Q_{\mathrm{geom},k} (\params) \\
&=& Q_{\mathrm{det},k}(\params) \,
    \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,
    R_{\star,k}\,T_k\,P^{-5/3} \quad.
\end{eqnarray}

>>>>

To measure the completeness of our long-period transit search method, we
exploit the fact that transit signals are sparse and rare.
Therefore, most light curves contain no transits and we can reliably measure
the recovery rate of our method on synthetic transit signals---with known
properties---injected into real light curves.
This procedure is standard practice in the transit literature and it has been
used to determine the completeness of the KOI catalog (\dfmtodo{cite}) and
other independent transit searches (\dfmtodo{cite}).

To reliably capture the full structure of the search completeness function,
the simulations must sample the (high-dimensional) space of all properties
that affect the probability of detecting a transit: the stellar properties
(including variability amplitudes and time scales), the planet's physical
properties and orbital elements, and any observational effects (noise,
spacecraft pointing variations, \etc).
For the modest goals of this paper, we only need a robust constraint on the
transit detection efficiency \emph{integrated} across the target sample but,
even so, many simulations per star are required.

The procedure for measuring the recovery rate of simulated transits is as
follows:
\begin{enumerate}
{\item First, a star is randomly selected from the target list, and the PDC
light curve and stellar properties for that star are loaded.}
{\item Planetary properties are sampled from the distributions listed in
\dfmtodo{some table} with phase uniformly distributed across the baseline of
observations. These properties are resampled until the transit is visible in
at least one non-flagged cadence.}
{\item The transit signal induced by this planet is computed and multiplied
into the PDC light curve.}
{\item The transit search method described in section \dfmtodo{some section}
(including de-trending and all automated vetting) is applied to this light
curve with the injected transit signal.}
{\item This candidate is flagged as recovered if at least one transit (within
\dfmtodo{some tolerance}) passes all the cuts imposed by the automated
vetting.}
\end{enumerate}

@@

\begin{eqnarray}
Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k}}{a_k(\params)}
    \, \frac{1 + e(\params)\,\sin\omega(\params)}{1-e(\params)^2} \\
&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}
    \, \left[\frac{1 + e(\params)\,\sin \omega(\params)}{1-e(\params)^2}\right]
    \, P^{-2/3}
\end{eqnarray}

@@

\begin{eqnarray}
Q_{\mathrm{temp},k} (\params) &=& \frac{T_k}{P}
\end{eqnarray}
where $T_k$ is the total observing baseline for target $k$.
Combined with the detection efficiency $Q_{\mathrm{det}}(\params)$ (assumed to
be constant for each target), the total completeness as a function of the
parameters is
\begin{eqnarray}
Q_k(\params) &=& Q_{\mathrm{det},k}(\params) \,
                 Q_{\mathrm{temp},k} (\params) \,
                 Q_{\mathrm{geom},k} (\params) \\
&=& Q_{\mathrm{det},k}(\params) \,
    \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,
    R_{\star,k}\,T_k
    \, \left[\frac{1 + e(\params)\,\sin \omega(\params)}{1-e(\params)^2}\right]
    \, P^{-5/3} \quad.
\end{eqnarray}
